Performance-portable Parallel Programming in Computer Science Education with Kokkos

### 2020-01-25 src/1.Introduction.tex
changes.

The rest of this paper is structured as follows. The next Chapter gives an overview on parallel programming concepts and presents the notion of \emph{semantic capture}. Chapter~\ref{chap:kokkosMM} presents the abstract machine model used to derive required semantic information for performance portability in Kokkos. Chapters~\ref{chap:kokkosPM} and ~\ref{chap:kokkosBackend} present the Kokkos programming model and its back-end support. Chapters~\ref{chap:c++} and~\ref{chap:related} show the alignment to C++ standardization efforts and discuss related work and lastly Chapter~\ref{chap:conclusion} concludes this work.

>>>>

The rest of this paper is structured as follows. The next Chapter gives an overview on parallel programming concepts and presents the notion of \emph{semantic capture}. Chapter~\ref{chap:kokkosMM} presents the abstract machine model used to derive required semantic information for performance portability in Kokkos. Chapters~\ref{chap:kokkosPM} and ~\ref{chap:kokkosExample} present the Kokkos programming model and an example application. In Chapter~\ref{chap:backend} provides insight into the Kokkos library implementation. Chapters~\ref{chap:c++} and~\ref{chap:related} show the alignment to C++ standardization efforts and discuss related work and lastly Chapter~\ref{chap:conclusion} concludes this work.
